Analysis : exp229 analysis

### 2018-11-21 resistingrhythm/analysis/exp229.Rmd
Update exp229 analysis

```{r}
results229 %>% 
  filter(osc_rate == "2") %>% 
  ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Frequency (Hz)", y="Pop. rate") 
```

>>>>

```{r}
results229 %>% 
  # filter(osc_rate == "2") %>% 
  ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Frequency (Hz)", y="Pop. rate") 
```
